### 2015-02-20 fundamentals/impl.tex
grammar and brevity

Version control preserves the development history, or \emph{provenance}, of
source code files. \Cyclus uses a well-established tool called git
\cite{software_freedom_conservancy_git_2014}
for this purpose. Git is currently the most popular utility in the recent wave
of \emph{distributed version control}. Briefly stated, this means that every
user has a complete local copy of the \emph{repository} (the version control
term for the collection of all possible histories).
One feature that git performs exceptionally well is \emph{branching}.
Branches are distinct pathways in the history that diverge from a mainline source
tree and then may be \emph{merged} back into the mainline. Multiple simultaneous
branches may exist at all points in time. Every change to the code is recorded
in the history, along with metadata such as the author, a timestamp, and an
accompanying message. Thus
it is possible for \Cyclus to accurately replay the entirety of who did what to the
code when.

>>>>

Version control preserves the development history, or \emph{provenance}, of
source code files. \Cyclus uses a well-established \emph{distributed version
control} tool called git \cite{software_freedom_conservancy_git_2014} for this
purpose.  Distributed version control allows every
user to have complete local copy of the \emph{repository} (the version control
term for the collection of all possible histories).
One feature that git performs exceptionally well is \emph{branching}.
Branches are distinct pathways in the history that diverge from a mainline source
tree and then may be \emph{merged} back into the mainline. Multiple simultaneous
branches may exist at all points in time. Every change to the code is recorded
in the history, along with metadata such as the author, a timestamp, and an
accompanying message. Thus
it is possible for \Cyclus to accurately replay the entirety of who did what to the
code when.
